---
title: "Two Parameters"
author: "Aaditya Gupta"
format: html
execute: 
  echo: false
---

```{r}
#| message: false

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
ch5 <- nhanes |>
filter(sex == "Male", age >= 18) |>
select(height) |>
drop_na()

ch5 |>
ggplot(aes(x = height)) +
geom_histogram(bins = 50) +
labs(title = "Male Adult Height in the US in 2010",
     x = "Height (cm)",
     y = "Count",
     caption = "Source: National Health and Nutrition Examination Survey")
```

```{r}
#| cache: true

fit_male_height <- brm(formula = height ~ 1, data = ch5, family = gaussian(), silent = 2, refresh = 0, seed = 12)
```

```{r}
#| label: plot

ndata <- tibble(.rows = 1)

fit_male_height |>
add_predicted_draws(newdata = ndata) |>
ggplot(aes(x = .prediction)) +
geom_histogram(aes(y = after_stat(count / sum(count))), bins = 100) +
labs(title = "Posterior for Height of Random Male",
     subtitle = "Uncertainty for a single individual is much greater than for the expected value",
     x = "Height (cm)",
     y = "Probability",
     caption = "Data source: NHANES") +
scale_x_continuous(labels = scales::number_format()) +
scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

We are using the nhanes data set from the National Health and Nutrition Examination Survey conducted from 2009 to 2011. We are trying to answer this question: What is the probability that the next man we meet will be taller than 180 centimeters? The model may not be representative enough. The data is being modeled on a histogram, with the dependent variable being the count. There is about a 30% chance that the next man we meet will be taller than 180 centimeters, with a confidence interval of about plus or minus 5%.

```{r}
fit_male_height |>
add_predicted_draws(newdata = ndata) |>
mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
summarize(odds = mean(tall))
```

```{r}
tbl_regression(fit_male_height, intercept = TRUE)
```
